---
title: "Credit Card Fraud Detection"
author: "Nitin Khandare"
date: "August 29, 2018"
output: html_document
---

```{r setup, include=FALSE}
library(randomForest)
library(e1071)
library(rpart)
library(rpart.plot)
library(caTools)
library(readr)
library(caret)
library(tidyverse)
library(caret)
library(VIM)
library(pROC)
library(ROCR)

card = read.csv('E:/Term 3/CaseStudies/Credit_Card_fraud_Detection/creditcard.csv')
knitr::opts_chunk$set(echo = TRUE)
```

### structure of Data
```{r}
str(card)
glimpse(card)
```

### Symmary of the Data
```{r}
summary(card)
```

### Check the Missing Values from Data
```{r}
colSums(is.na(card))

aggr(card)

```

### Check the correlation between Columns
```{r}
num = sapply(card, function(x) is.numeric(x) & length(unique(x))>1)
corrplot(cor(card[,num]),order = 'hclust')
```


```{r}

```

### Percentage of outlier
```{r}

PerOutier = function(df){
  num=sapply(df, is.numeric)
  NumOut = function(x){
    q1 = quantile(x, 0.25, na.rm = T)
    q2 = quantile(x, 0.50, na.rm = T)
    q3 = quantile(x, 0.75, na.rm = T)
    iqr = q3-q1
    outlier = x[x > q3 + 1.5*iqr | x < q1 - 1.5*iqr]
    percent = (length(outlier) / length(x))*100
return(percent)
  }
  data=sapply(df[,num], NumOut)
   return(as.data.frame(data))
}

PerOutier(card)
```

#### Check the oultier from Data
```{r}

boxplot(card)
```

### Convert target Variable as a factor
```{r}
card$Class = as.factor(card$Class)
```

### To Pre-Process and Normalize data
```{r}
preObj <- preProcess(card[,-31], method=c("scale","center"))
newData <- predict(preObj, card[, -31])
```


############################################################################################
#################################### Predictive Modelling ##################################
############################################################################################

### Sampling the Data in Train And Test
```{r}

#### Random Sampling
set.seed(101)

train = card[sample(seq(1,nrow(card)),(0.7*nrow(card))),]

test = card[sample(seq(1,nrow(card)),(0.3*nrow(card))),]
```

### Dimention of Data

```{r}
dim(train)

dim(test)
```


### Decision tree model
```{r}
test$Class = as.factor(test$Class)

## tree model fitting
model.tree = rpart(Class~., data = train, method = 'class', minbucket = 20) 

### get the plot of tree splitting using rpart.plot
rpart.plot(model.tree)


### Prediction on test data
tree.predict <- predict(model.tree, test, type = "class")


### Confusion matrix to get the tabular representation of Actual and Predicted Value
confusionMatrix(test$Class, tree.predict,positive = "1")

```


### model fitting using Logistic Regression
```{r}
glm.model <- glm(Class ~ ., data = train, family = "binomial", control = list(maxit = 50))

glm.predict <- predict(glm.model, test, type = "response")

table(test$Class, glm.predict > 0.5)

summary(glm.model)
```


### Random forest Model
```{r}
### get the mtry parameter for random forest

# mtry = round(sqrt(length(names(train))))

set.seed(1)

model.rf = randomForest(Class~., data = train, ntree = 2000, nodesize = 20)

predict.rf = predict(model.rf, test, type = 'prob')

test$pred_class = ifelse(predict.rf[,2]>0.5, 1, 0)

test$pred_class = as.factor(test$pred_class)

confusionMatrix(test$Class, test$pred_class)
```


#### ROC curve for performace Evaluation
```{r}
roc_rf = roc(test[,Class],predict.rf[,2])

plot(roc_rf)
```

```{r}

```

