---
title: "Washington_State_Home_Loan_Analysis"
author: "Nitin Khandare"
date: "August 31, 2018"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(readr) 
library(RColorBrewer)
library(ggthemes)
library(corrgram)
library(VIM)
hp = read.csv("E:/Term 3/CaseStudies/Washington_State_HDMA-2016/Washington_State_HDMA-2016.csv")
knitr::opts_chunk$set(echo = TRUE)
```


## Structure of the data
```{r}
str(hp)
```


### Summary of the Data
```{r}
summary(hp)
```


### check the missign values NA values from the Data
```{r}
colSums(is.na(hp))
```

```{r}
#impute missing values with median
hp$rate_spread[is.na(hp$rate_spread)] <- median(hp$rate_spread, na.rm = TRUE)

#impute 0 with median
combi$Item_Visibility <- ifelse(combi$Item_Visibility == 0, median(combi$Item_Visibility),                                   combi$Item_Visibility)

#find mode and impute
table(combi$Outlet_Size, combi$Outlet_Type)
evels(combi$Outlet_Size)[1] <- "Other"
```

#### Missing value treatment from the Data using median
```{r}


impute_BY_Median <- function(df){
  num = sapply(df, is.numeric)
  imp = function(x){
  ind_na <- is.na(x)
  if(sum(ind_na)/length(x) < 0.4){
    x[ind_na] <- median(x[!ind_na])
  }
  return(x)
  }
  return(as.data.frame(sapply(df[,num], imp)))
}

new_hp = impute_BY_Median(hp)

colSums(is.na(hp))


VIM::aggr(hp)


```

### Remove higher outlier column and high missing value Column. (if both are there just discard it)
```{r}

whp = hp_new %>% select(-rate_spread)

colSums(is.na(whp))

PerOutier(whp)

```




### Check the level of outliers in every column of Data
```{r}
boxplot(whp)
```


### check the Percentage of outlier in data column vise
```{r}

PerOutier = function(df){
  num=sapply(df, is.numeric)
  NumOut = function(x){
    q1 = quantile(x, 0.25, na.rm = T)
    q2 = quantile(x, 0.50, na.rm = T)
    q3 = quantile(x, 0.75, na.rm = T)
    iqr = IQR(x, na.rm = T)
    outlier = x[x < q1 - 1.5 * iqr | x > q3 + 1.5 * iqr]
    percent = (length(outlier) / length(x))*100
return(percent)
  }
  data=sapply(df[,num], NumOut)
   return(as.data.frame(data))
}
PerOutier(hp)

```



```{r}

### outlier treatment for application_income column
{{quantiles1 = quantile(whp$applicant_income_000s, probs = c(.25, .75),na.rm = T)

range1 = 1.5 * IQR(whp$applicant_income_000s,na.rm = T)

normal_hp = subset(whp,whp$applicant_income_000s > (quantiles1[1] - range1) & whp$applicant_income_000s < (quantiles1[2] + range1))}}


### outlier treatment for sequence_number 

{{quantiles2 = quantile(normal_hp$sequence_number,probs = c(.25, .75),na.rm = T)

range2 = 1.5 * IQR(normal_hp$sequence_number,na.rm = T)

normal_hp = subset(normal_hp,normal_hp$sequence_number > (quantiles2[1] - range2) & normal_hp$sequence_number < (quantiles2[2] + range2))}}


### outlier treatment for census_tract_number

{{qunatiles3 = quantile(normal_hp$census_tract_number,probs = c(0.25, .75),na.rm = T)

range3 = 1.5 * IQR(normal_hp$census_tract_number, na.rm = T)

normal_hp = subset(normal_hp,normal_hp$census_tract_number > (qunatiles3[1] - range3) & normal_hp$census_tract_number < (qunatiles3[2] + range3))}}


PerOutier(normal_hp)
```



### WE Get the clean Data after NA values and Outlier treatment
```{r}
aggr(normal_hp)

```

### Plotting of the Data
```{r}
hp %>%
  group_by(loan_purpose_name) %>%
  summarise(Count = n()) %>%
  arrange(desc(Count)) %>%
  ggplot(aes(reorder(loan_purpose_name, Count), y = Count, fill = Count)) + 
  geom_bar(stat ='identity') +  
  coord_flip() +
  theme_fivethirtyeight() + 
  theme(legend.position ='none', axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 20)) +
  scale_fill_gradientn(name = '',colours = rev(brewer.pal(10,'Spectral'))) +
  ggtitle('Loan Purpose Counts')
```

```{r}
ggplot(hp, aes(x=population)) + 
  geom_density() + 
  theme(legend.position="none") +
  ylab("Density") +
  xlab("Population") + 
  ggtitle("Population Density") + 
  geom_vline(aes(xintercept=mean(population)), color="blue", linetype="solid", size=1) 
```

